Data_visualization

### 2018-09-10 Rmd/Data_visualization_common_names.Rmd
common names
TOTAL POLLEN PLOTS

@@

tab <- read.csv("Data/tab.csv", sep="", header = T)

>>>>

\newpage
###TOTAL POLLEN ON STIGMA -NEXT 3 PAGES-
```{r, message=FALSE, warning=FALSE, echo=FALSE,fig.width=8}
total_pollen_brassicaceae <- read.csv("Data/total_pollen_brassicaceae.csv", header=T)

ggplot(total_pollen_brassicaceae, aes(x=spp, y=ratio, fill=variable)) +
  geom_bar(stat='identity', position='dodge') +labs(title="Brassicaceae", x="", y="Pollen grains on stigma") + 
  theme(axis.text.x=element_text(angle=60,hjust=1))+
  scale_fill_manual(values=c("grey10", "grey60"))

\newpage
```{r, message=FALSE, warning=FALSE, echo=FALSE,fig.width=8}

total_pollen_solanaceae <- read.csv("Data/total_pollen_solanaceae.csv", header=T)

ggplot(total_pollen_solanaceae, aes(x=spp, y=ratio, fill=variable)) +
  geom_bar(stat='identity', position='dodge') +labs(title="Solanaceae", x="", y="Pollen mix ratio") +
  theme(axis.text.x=element_text(angle=60,hjust=1))+
  scale_fill_manual(values=c("grey10", "grey60"))

```
\newpage

```{r, message=FALSE, warning=FALSE, echo=FALSE,fig.width=8}

total_pollen_convolvulaceae <- read.csv("Data/total_pollen_convolvulaceae.csv", header=T)

ggplot(total_pollen_convolvulaceae, aes(x=spp, y=ratio, fill=variable)) + 
  geom_bar(stat='identity', position='dodge') +labs(title="Convolvulaceae", x="", y="Pollen mix ratio") + 
  theme(axis.text.x=element_text(angle=60,hjust=1))+
  scale_fill_manual(values=c("grey10", "grey60"))

@@

tab <- read.csv("Data/tab_common_names.csv", sep="", header = T)
